Introduction

### 2016-04-29 dissertation/introdefhistory.tex
small corrections

The following challenges several conventions of scientific
writing. Passive voiced is generally overused in scientific writing,
sometimes because the author may think it emphasises the objectivity
of the investigation. In my opinion it rather attempts to hide the
fact that science is a human and social endeavour, and only by
acknowledging that fact, an investigator can properly account for
their own role. Double blind trials in medicine are an example of why
it is important to acknowledge the investigators role. Moreover, the
use of ``we'', when it is clear that the work has been done by a
single investigator is inappropriate as it is attempting to obscure
the role of the investigator.

As noted, the Semantic Web is a complex technical, social, economic
and cultural artefact. The objectivity of an investigator may be
challenged by a large intellectual investment in this artefact, the
more you want this artefact to succeed, the higher your risk of not
being sufficiently objective is. I hereby proclaim that I have a very
large intellectual investment in the success of the Semantic Web, and
therefore this section is a reflection on my own role in the
development of this artefact.

@@

However, it became clear that I could not have sufficient time in the
industry to pursue what was developing as my main interest, query
answering over data on the open Web, for generic application
development. 16 years of experience thus motivates the research done
in this thesis.

>>>>

The following challenges several conventions of scientific
writing. Passive voiced is generally overused in scientific writing,
sometimes because the author may think it emphasises the objectivity
of the investigation. In my opinion it rather attempts to hide the
fact that science is a human and social endeavour, and only by
acknowledging that fact, an investigator can properly account for
their own role. Double blind trials in medicine are an example of why
it is important to acknowledge the investigators role. Moreover, the
use of ``we'', when it is clear that the work has been done by a
single investigator is inappropriate as it obscures
the role of the investigator.

As noted, the Semantic Web is a complex technical, social, economic
and cultural artefact. The objectivity of an investigator may be
challenged by a large intellectual investment in this artefact, the
more you want this artefact to succeed, the higher may your risk of not
being sufficiently objective be. I hereby declare that I have a very
large intellectual investment in the success of the Semantic Web, and
therefore this section is a reflection on my own role in the
development of this artefact.

@@

However, it became clear that I could not have sufficient time in the
industry to pursue what was developing as my main interest, query
answering over data on the open Web, for generic application
development.

While the motivation and the problem statements of this work
undoubtedly have been influenced by my intellectual investment in the
Semantic Web, the papers will show that the evaluation has not.
